caDDS: Community Assisted Distributed Database for Sequences

### 2020-06-25 Paper2020ACM/Presentation.tex
Thesis submission June 25 6pm

    \begin{frame}{Distributed: SeqTorr}
        Problems: 
        \begin{itemize}
            \item System not currently available
            \begin{itemize}
                \item cOnly exists documentation of their APIs
            \end{itemize}
        \end{itemize}
    \end{frame}

@@

\section{Problem}
% after discussion of dist. databases
\begin{frame}{Problem}
    The different gaps or problems found with other implementations
    \textbf{Problems of Classical Databases}
    %PROBLEMS OF CLASSICAL DATABASES (ALL FOUR)
    \begin{enumerate}
        \item Genome researchers download an entire database of genomics data, especially when uncertain how to update their data
        \item Genome researchers only need a portion of the database, but end up downloading the entire database
        \item Client-Server approach can face bottlenecks (server speed) (Section \ref{client-server})
        \item P2P approach has a need of a large unmoderated active user base to work (Section \ref{p2p})
    \end{enumerate}
    \textbf{Problems of Distributed Databases}

@@

\begin{frame}{Theoretical Framework: System Description}
    \begin{itemize}
        \item A \textbf{master node} stores metadata of all sequences, may or may not contain sequence files
        \item \textbf{Data nodes} stores sequence files \& metadata of all sequence files in its filesystem
        \item Both master node \& data nodes have user interface that allow users to upload, search, and download sequence files
    \end{itemize}
\end{frame}

% DRAW.IO FILE: https://drive.google.com/file/d/1Nbp0Kmgcr2BZ13LBT3SGLMBoA6JA_Eth/view
\begin{frame}{Theoretical Framework: Schematics}
\textbf{App network diagram} \\ \medskip
\centering
\includegraphics[scale=0.5]{thesis1.png}
\end{frame}

\begin{frame}{Theoretical Framework: Schematics}
\textbf{POST: Uploading a sequence to the master node} \\ \medskip
\centering
\includegraphics[scale=0.5]{thesis3.png}
\end{frame}

\begin{frame}{Theoretical Framework: Schematics}
\textbf{POST: Uploading a sequence to a data node} \\ \medskip
\centering
\includegraphics[scale=0.5]{thesis2.png}
\end{frame}

\begin{frame}{Theoretical Framework: Schematics}
\textbf{GET: Downloading a sequence} \\ \medskip
\centering
\includegraphics[scale=0.5]{thesis4.png}
\end{frame}

@@

\subsection{System Summary}
\begin{frame}{System}
  \begin{itemize}   
    \item 
    \item 
    \item 
  \end{itemize}
\end{frame}

>>>>

    \begin{frame}{Distributed: SeqTorr}
        Problems: 
        \begin{itemize}
            \item System not currently available
            \begin{itemize}
                \item Only exists documentation of their APIs
            \end{itemize}
        \end{itemize}
    \end{frame}

@@

\section{Problem}
% after discussion of dist. databases
\begin{frame}{Problem}
    The different gaps or problems found with other implementations
    \textbf{Problems of Classical Databases}
    %PROBLEMS OF CLASSICAL DATABASES (ALL FOUR)
    \begin{enumerate}
        \item Genome researchers download an entire database of genomics data, especially when uncertain how to update their data
        \item Genome researchers only need a portion of the database, but end up downloading the entire database
        \item Client-Server approach can face bottlenecks (server speed)
        \item P2P approach has a need of a large unmoderated active user base to work
    \end{enumerate}
    \textbf{Problems of Distributed Databases}

@@

\begin{frame}{Theoretical Framework: System Description}
    \begin{itemize}
        \item The system is inspired by SeqTorr's design
        \item A \textbf{Master node} does administrative functions: authentication, uploading, moderation. It also contains all metadata.
        \item \textbf{Data nodes} stores sequence files \& metadata of all sequence files in its filesystem
    \end{itemize}
\end{frame}
\begin{frame}{Theoretical Framework: System Description}
    When a user downloads a sequence:
    \begin{itemize}
        \item The user searches for keywords in the system
        \item The user is then given the results and the available data nodes
        \item The user then chooses to download from one data node or from multiple data nodes
    \end{itemize}
\end{frame}

% DRAW.IO FILE: https://drive.google.com/file/d/1Nbp0Kmgcr2BZ13LBT3SGLMBoA6JA_Eth/view
\begin{frame}{Theoretical Framework: Schematics}
\textbf{App network diagram} \\ \medskip
\centering
\includegraphics[scale=0.5]{images/thesis1.png}
\end{frame}

\begin{frame}{Theoretical Framework: POST}
\textbf{POST: Uploading a sequence} \\ \medskip
\centering
\includegraphics[scale=0.50]{images/thesis1-Page-3.png} 
\end{frame}

\begin{frame}{Theoretical Framework: GET}
\textbf{GET: Downloading a sequence} \\ \medskip
\centering
\includegraphics[scale=0.5]{images/thesis4.png}
\end{frame}

\begin{frame}{Theoretical Framework: PUT}
\textbf{PUT: Updating a sequence} \\ \medskip
\centering
\includegraphics[scale=0.5]{images/thesis1-Page-5.png}
\end{frame}

\begin{frame}{Theoretical Framework: DELETE}
\textbf{DELETE: Deleting a sequence} \\ \medskip
\centering
\includegraphics[scale=0.5]{images/thesis1-zzzzz.png}
\end{frame}

@@
